Mining the human microbiome for clinical insight

### 2019-01-25 acknowledgments.tex
Update acks

Beyond the work presented in these pages, I spent a significant portion of my PhD in student leadership roles in my department and at MIT.
Learning conflict management skills as a BE REF positively impacted almost every aspect of my life.
This impact wouldn't have happened without the people involved in my early REFS days: Libby Mahaffy, Scott Olesen, Georgia Lagoudas, T\'{u} Nguyen, Deena Rennerfeldt, and Souparno Ghosh.
I also thank my early diversity co-conspirators, Scott Olesen and Manu Kumar, for sharing in my rants and helping me channel my passions toward productive change.
Amanda Facklam was also key to getting the BE Application Assistance Program up and running, and I thank her for her sustained support and enthusiasm for this exciting initiative.
I was able to grow tremendously as a student leader because of our receptive departmental leadership, and I am very thankful to Doug Lauffenburger for being thoughtful, supportive, and responsive to our efforts.
My current GSC diversity crew, Nasir Almasri, Josu\'{e} Lop\'{e}z, Danielle Orozco Cos\'{i}o, German Parada, Halston Lim, and Bianca Lepe, revitalized me in this work when I was closest to burning out.
The future of diversity and equity at MIT is bright if they are leaders in it.
Similarly, I am grateful for the brief time I overlapped with Jess Boles and Parker Vascik in GradSAGE, and am excited to watch them positively transform the culture of advising at MIT.

Finally, I thank my friends, family, and frisbee teammates for keeping me happy and healthy during my PhD.
I cannot thank Carolyn Saund and Megan Armstrong enough for being right by my side these past years, for supporting my growth, and for growing alongside me as we figure out how to maneuver this world.
Hold on tight to your passion, and thanks in advance for reminding me to do the same.
When I think about strong support networks of badass women, Andee Wallace and Shelby Doyle also come to mind.
Maneuvering grad school together enriched my experience tremendously, kept me focused on what matters, and was a lot of fun.
Thanks also to Brett Geiger, the BE 2014 cohort, and the entire BE community for being great friends and colleagues.
I am also thankful to Janyne Little, who keeps me adventuring and reminds me about the world outside my urban ivory towers.
Jeremy Pivor moving back to Boston was pivotal for my happiness in this city: I am so lucky for his friendship and treasure his radiant soul.
I've also been lucky to share living spaces with incredibly supportive and friendly roommates: Kunal Bhutani, a man kinder and more thoughtful than I will ever be, and the 9 Seattleites, including my dear childhood friend (and yet another badass woman inspiration) Kelly Moynihan, as well as Khoi Nguyen, Andee Wallace, Ashvin Bashyam, Griffin Clausen, Santiago Correa-Echevarria, Shawn Musgrave, and of course Nancy, Barb, Sonia, and Ruth.

To everyone I have ever thrown a frisbee with: thank you for keeping me physically and mentally healthy. I am especially grateful to have been a member of sMITe, MIT's women's ultimate frisbee team, during my entire PhD. I treasure having had the opportunity to learn about MIT's fascinating undergraduate culture and to witness the transformation of so many young women into confident players and leaders. Lisa, Bethany, Margalit, Julia, Abby, Oreo, Kimmy, Kelly, Helen, Michelle, Mary, Amy, Theresa, Sam, Ivana, and everyone else on sMITe: thanks for putting up with me, and for being my friend.

>>>>

Beyond the work presented in these pages, I spent a significant portion of my PhD in student leadership roles in my department and at MIT.
Learning conflict management skills as a BE REF positively impacted almost every aspect of my life.
This impact wouldn't have happened without the people involved in my early REFS days: Libby Mahaffy, Scott Olesen, Georgia Lagoudas, T\'{u} Nguyen, Deena Rennerfeldt, and Souparno Ghosh.
I also thank my early diversity co-conspirators, Scott Olesen and Manu Kumar, for sharing in my rants and helping me channel my passions toward productive change.
Amanda Facklam was also key to getting the BE Application Assistance Program up and running, and I thank her for her sustained support and enthusiasm for this exciting initiative.
I was able to grow tremendously as a student leader because of our receptive departmental leadership, and I am very thankful to Doug Lauffenburger for being thoughtful, supportive, and responsive to our efforts.
My current GSC diversity crew, Nasir Almasri, Josu\'{e} Lop\'{e}z, Danielle Orozco Cosio, German Parada, Halston Lim, and Bianca Lepe, revitalized me in this work when I was closest to burning out.
The future of diversity and equity at MIT is bright if they are leaders in it.
Similarly, I am grateful for the brief time I overlapped with Jess Boles and Parker Vascik in GradSAGE, and am excited to watch them positively transform the culture of advising at MIT.

Finally, I thank my friends, family, and frisbee teammates for keeping me happy and healthy during my PhD.
I cannot thank Carolyn Saund and Megan Armstrong enough for being right by my side these past years, for supporting my growth, and for growing alongside me as we figure out how to maneuver this world.
Hold on tight to your passion, and thanks in advance for reminding me to do the same.
When I think about strong support networks of badass women, Andee Wallace and Shelby Doyle also come to mind.
Maneuvering grad school together enriched my experience tremendously, kept me focused on what matters, and was a lot of fun.
Thanks also to Brett Geiger, the BE 2014 cohort, and the entire BE community for being great friends and colleagues.
I am also thankful to Janyne Little, who keeps me adventuring and reminds me about the world outside my urban ivory towers.
Jeremy Pivor moving back to Boston was pivotal for my happiness in this city: I am so lucky for his friendship and treasure his radiant soul.
I've also been lucky to share living spaces with incredibly supportive and friendly roommates: Kunal Bhutani, a man kinder and more thoughtful than I will ever be, and the 9 Seattleites, including my dear childhood friend (and yet another badass woman inspiration) Kelly Moynihan, as well as Khoi Nguyen, Andee Wallace, Ashvin Bashyam, Griffin Clausen, Santiago Correa, Shawn Musgrave, and of course Nancy, Barb, Sonia, and Ruth.

To everyone I have ever thrown a frisbee with: thank you for keeping me physically and mentally healthy. I am especially grateful to have been a member of sMITe, MIT's women's ultimate frisbee team, during my entire PhD. I treasure having had the opportunity to learn about MIT's fascinating undergraduate culture and to witness the transformation of so many young women into confident players and leaders. Lisa, Bethany, Margalit, Julia, Abby, Oreo, Kimmy, Kelly, Helen, Michelle, Mary, Amy, Theresa, Sam, Ivana, Maddi, Cynthia, Serena and everyone else on sMITe: thanks for putting up with me, and for being my friend.
